Statistical Inference of Transport Mechanisms and Long Time Scale Behavior from Time Series of Solute Trajectories in Nanostructured Membranes

### 2020-07-13 Ben_Manuscripts/stochastic_transport/response_to_reviewers.tex

  % comment 2  
  \item \textit{\textbf{MD-section} \\
        \textbf{Page 8 and 9} \\
        The authors refer to ref 13 (where these simulations have been performed before), 
        nevertheless I find that the MD section does not provide sufficient amount of details 
        to be self-contained. Could the authors specify the force field, as well as summarize 
        its reliability for this particular system (often simulations involving changed solutes
        through pores require polarizable force fields)?
   }

  Author reply: We thank the reviewer for pushing us to include more details about our 
  molecular simulations in order to boost reproducibility. The length of the manuscript made
  us wary to include information that could be accessed elsewhere, however there are 
  benefits to keep this very important section self-contained.

  We added the following text to address comments related to our choice of force field:

  New text:
  \begin{quote}
  We modeled water molecules using the TIP3P water model,~\cite{jorgensen_comparison_1983}
  We used the Antechamber module shipped with AmberTools18 to parameterize monomers and 
  solutes using the Generalized Amber Force Field (GAFF).~\cite{wang_development_2004} We 
  assigned charges using the AM1-BCC model.~\cite{jakalian_fast_2000,jakalian_fast_2002}
  GAFF is very commonly used in simulations with diverse organic chemical functionality, 
  and was developed for consistency within the AMBER ecosystem, which uses TIP3P as the
  water model. We chose these standard force fields and generalizable parameterization 
  approaches so that a range of solutes and monomers could be self-consistently and easily 
  studied. The main goal of this work is to develop stochastic models which can reproduce
  solute behavior on MD time scales, independent of the choice of force field. In future 
  work, it may be beneficial to employ specialized force fields, including polarizable 
  force fields or other higher-order effects in order to improve the accuracy of structure 
  parameters and selectivity predictions.
  \end{quote}

@@

        Original text:
        \begin{quote}
        We do not consider the two mode AD model because it has a broken correlation structure 
        and we do not consider the MSDDM because its realizations do not display the expected 
        hopping and trapping behavior. 
        \end{quote}

        New text:
        \begin{quote}
        Although it would be trivial to test the two mode model as well, we chose not to because
        we feel the results would be misleading to the reader since the stochastic trajectories
        generated by this method lack a firm physical basis as discussed in Section~\ref{M-section:AD_all_data}. 
        We also do not consider the MSDDM because its realizations do not display the expected 
        hopping and trapping behavior. 
        \end{quote}

  % comment 9
  \item \textit{\textbf{Page 35 line 20-42:}\\
        A pore-length of 50 nm is a little underwhelming compared to 7 micrometers. Reading the paper
		I do not understand what lies behind this limitation - what hinders the sampling one really would
		like to have when doing such modeling? Also, you write about RAM-requirements scaling more
		than linearly (assuming with L). What exactly lies behind this scaling? Finally, just out of
		curiosity, are there ways of coarse-graining/renormalizing the random walk such that larger time
		and length scales can be reached? That being said, I am impressed by fit against the scaling
	  	law.}

	  	Author reply: We can appreciate why the reviewer has questioned this limitation.
		When simulating fractional motion, each step must be correlated to all of its previous 
		steps. Therefore the computational cost increases with each added step. We show in the paper
		that the mean first passage time across the pores scales with L$^{\alpha}$, and $\alpha$ is
		always $\geq$ 2. As the degree of anti-correlation between hops increases, the scaling
		parameter also increases. Therefore, we need to generate very long trajectories, with 
		correlation between all data points, in order to sufficiently sample the MFPT distribution 
		before fitting them to Equation 9. This is especially challenging with slow-moving solutes
		like acetic acid. We needed to simulate over 2 million time steps in order to sufficiently
		sample the MFPT over a 50 nm pore. This procedure becomes computationally expensive very
		quickly, and requires ample RAM to store the trajectories as they are constructed.

@@

	  	This may be an issue that could be overcome by developing specialized algorithms and perhaps 
	  	by using a compiled computer language like C++.

        We have modified the text to express the current limitations in a more straightforward manner:

	  	Original text:
	  	\begin{quote}
	  	The RAM requirements and performance scales greater than linearly and thus would take an 
	  	infeasible amount of memory and time to simulate transport through a pore over 100 times
        longer. 
	  	\end{quote}

	  	%MRS: scanning over this, it's probably more important to say that we probably didn't need to do it, since
                %the analytical fit was so good.
	  	Modified text:
	  	\begin{quote}
	  	At this time, it is infeasible for us to simulate transport through a pore over 100 times
	  	longer without investing significant effort into writing and optimizing new code that can
	  	handle simulation of large trajectories with correlation between all steps.
	  	\end{quote}

@@

\end{enumerate}

\bibliographystyle{ieeetr}
\bibliography{stochastic_transport}

\end{document}

% LocalWords:  Subdiffusive Solute Nanoscale Coscia leftmargin FBM vy
% LocalWords:  subdiffusion CTRW sFBM ref solutes antechamber solute
% LocalWords:  polarizable LLC intramolecular quasiharmonic BJC JCTC
% LocalWords:  tex fontsize evy Methanol's selectivities MSDDM arXiv
% LocalWords:  parametrization MSDs MSD timescales renormalizing MFPT
% LocalWords:  bicontinuous Donnan steric em dt lyotropic
% LocalWords:  subdiffusive

### 2020-08-01 Ben_Manuscripts/hdphmm/response_to_reviewers.tex

\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{xr}
\usepackage{xcolor}
\usepackage{siunitx}
\usepackage{gensymb}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{scrextend}
\usepackage[normalem]{ulem}

\externaldocument[S-]{Supporting_Information}
\externaldocument[M-]{Final_Draft}

\begin{document}

\graphicspath{{./figures/}}

\begin{center}
\textbf{Response to reviewers: Statistical Inference of Transport Mechanisms and Long
        Time Scale Behavior from Time Series of Solute Trajectories in Nanostructured Membranes} \\
Authors: Benjamin J. Coscia, Christopher P. Calderon and Michael R. Shirts
\end{center}

We thank the reviewers for carefully reading over our manuscript and providing
thoughtful and constructive feedback. We have taken the suggestions into consideration 
and made appropriate revisions to the manuscript document. The comments have been reproduced
in italics and all changes to the text have been documented below them. Any newly added
references are given in the bibliography of this document and are placed in the main 
text with appropriate numbering.

\section*{Response to Reviewer 1}

\begin{enumerate}[label={Comment \theenumi :}, leftmargin=3.9\parindent]

    \item \textit{The manuscript by Coscia et al. analyzes diffusion and transport of solute molecules
    in a low water content lyotropic liquid crystal using a statistical model developed on the basis 
    of molecular dynamics simulations. The purpose of the statistical model is two-fold; first to 
    extrapolate computed MSDs to longer times to obtain diffusion coefficients, and second to attempt
    to gain increased physical insight on diffusion mechanisms. These issues are important in 
    highly-confined/low-water content nanoporous materials, in which diffusion occurs through complex
    mechanisms and over long timescales. The manuscript will most likely be of interest to the community
    interested in nanoporous materials for separations.}

    Author reply:

    \item \textit {Unfortunately, because there is no comparison with alternative techniques, it is 
    very difficult to evaluate this new approach relative to previous work that has examined similar 
    issues. There exist numerous other methods for extrapolating MSDs to longer time, which the 
    authors have not discussed. One such method is the “trajectory-extending kinetic Monte Carlo” 
    (TEKMC) approach of Brown and coworkers see e.g. Macromolecules 2010, 43, 9210-9214, 
    Macromolecules 2015, 48, 7346-7358, and J. Phys Chem. B, 2012, 116, 95-103. The authors should 
    add a comprehensive discussion of how their approach compares to this and similar methods. The 
    paper would be significantly improved if the authors were to perform and present TEKMC results 
    for their system, so that one could better evaluate the performance of their proposed method.}

    Author reply:

    %BJC: not sure if I should ignore the JCTC part completely or basically just say what the editor said.
    \item \textit{Much of the writing seems more suitable for JCTC rather than JPC. I encourage the
    authors to better emphasize and discuss “new physical insight” and “chemical details”, and spend
    less time on methodology. For example pages 5-16 are all on methodology, yet it is not until 
    Figure 8 of the paper (page 26) that the authors give any description of what the LLC system 
    they are studying is actually composed of. Presumably the LLC is made up of self-assembled 
    monomers (in water) shown in Figure 8a). I would encourage the authors to describe their 
    system more concretely much earlier in the paper... there is also no information on system 
    size, box dimensions, etc.}

    Author reply: We thank the reviewer for pushing us to include more details about our 
  molecular simulations in order to boost reproducibility. The length of the manuscript made
  us wary to include information that could be accessed elsewhere, however there are 
  benefits to keep this very important section self-contained.

  We added the following text to address comments related to our choice of force field:

  New text:
  \begin{quote}
  We modeled water molecules using the TIP3P water model,~\cite{jorgensen_comparison_1983}
  We used the Antechamber module shipped with AmberTools18 to parameterize monomers and 
  solutes using the Generalized Amber Force Field (GAFF).~\cite{wang_development_2004} We 
  assigned charges using the AM1-BCC model.~\cite{jakalian_fast_2000,jakalian_fast_2002}
  GAFF is very commonly used in simulations with diverse organic chemical functionality, 
  and was developed for consistency within the AMBER ecosystem, which uses TIP3P as the
  water model. We chose these standard force fields and generalizable parameterization 
  approaches so that a range of solutes and monomers could be self-consistently and easily 
  studied. The main goal of this work is to develop stochastic models which can reproduce
  solute behavior on MD time scales, independent of the choice of force field. In future 
  work, it may be beneficial to employ specialized force fields, including polarizable 
  force fields or other higher-order effects in order to improve the accuracy of structure 
  parameters and selectivity predictions.
  \end{quote}

  % comment 4      
  \item \textit{Lastly, it would be natural to report the size of the system in this
              section (I found it eventually in the introduction after searching for it 
              throughout the manuscript).}

              Author reply:

              We thank the reviewer for pointing out this missing piece of information. We
              have added the following text in order to inform the reader of the system's size:
			  \begin{quote} 
			  Each unit cell contains $\sim$ 62,000 total atoms.
			  \end{quote}

    Author reply:

    \item \textit{The authors should more clearly note that their discussion largely applies only 
    to very low water content LLC regimes (such as the 10\% LLC studied). For higher water content 
    LLCs (e.g. > 15-20\%) it is straightforward to obtain the diffusion limit from standard MD 
    simulations. While the authors are surely well aware of this, the reader may not be, and it is
    important to clearly distinguish the regimes.}

    \item \textit{In the HDP-AR-HMM method, it is not clear to me how the solute molecules are 
    constrained to be confined within the pore radius (which they must be on physical grounds 
    based on steric interactions). From Figure 2, it “looks” like this happens to work out, but
    for more complicated systems (e.g. gyroid LLCs with 3D channels) such a constraint may be 
    necessary and it is unclear how the method would generalize. This should be discussed.}

    \item \textit{As stated in the introduction, one motivation for the work is that “...one 
    cannot reliably compute diffusion constants because MSDs are often non-linear on the timescales
    accessible to molecular simulation”. Later on in section 2.4, the authors state “For the 
    purposes of our analysis, we assume ergodicity of the 24 solute trajectories.” These are 
    contradictory statements. If the trajectories are ergodic, then MSDs will be linear by 
    definition The authors should clarify. Similarly, in Figure 7, if the simulations are indeed 
    ergodic the red and blue bars should be proportional to each other.}

    \item \textit{There are no units on Figure 1 y-axis, presumably these are nanometer like the 
    other figures?}

    \item \textit{Figure captions need to be improved. Wording such as “we plotted...”, “we 
    calculated...”, “We also analyzed...” should be omitted in figure captions.}

%  Original text:
%  \begin{quote}
%  We treat our system in terms of two well-known classes of anomalous subdiffusion: 
%  \end{quote}
%  
%  New text:
%  \begin{quote}
%  In this first approach, we treat our system in terms of two well-known types of molecular
%  motion which lead to anomalous subdiffusion: 
%  \end{quote}

  \end{enumerate}

\section*{Response to Reviewer 2}

\begin{enumerate}[label={Comment \theenumi :}, leftmargin=3.9\parindent]

    %r2_comment1
    \item \textit{This paper presents an approach to study transport mechanisms of solutes within
    membranes by applying the sticky hierarchical Dirichlet process autoregressive hidden Markov model
    (HDP-AR-HMM) to molecular dynamics simulation trajectories spanning long times (5 microseconds). 
    Using this method, the authors reveal different dynamic states associated with the transport of 
    solute across a membrane, and interpret them on the basis of solute-membrane interactions. The 
    paper is clear, well written, and relevant to the Journal of Physical Chemistry. I only have a 
    couple of suggestions and minor corrections:}

    Author reply: We thank the reviewer for their kind assessment of our work.

    %r2_comment2
    \item \textit{A motivation for the study is providing a computational tool to guide experimentalists
    in designing membrane materials. However, given the length of the molecular dynamics simulations 
    required, it is presumably impractical to carry a large-scale screening in this way. It would be 
    useful if the authors were more explicit about the role of this approach in guiding experiments, 
    and what would be its advantages and limitations compared to a purely experimental search.}

    Author reply: We thank the reviewer for pushing us to further evaluate the practicality of our
    method as a tool for experimentalists. In short, there are many ways we can envision that 
    would make this approach more amenable to high throughput simulations. The length of our 
    simulations in this paper are indeed quite long. The dynamics of the solutes are somewhat 
    slow and we wanted to ensure we gathered enough data for a sufficient parameterization. 
    Putting aside brute force high throughput simulations that could be enabled by the 
    ever-increasing availability of HPC resources, it would be to our benefit to use the system
    in this work as a benchmark to explore much less expensive models.
    %BJC: I'm not exactly sure where to put this. Originally I thought conclusions because it's
    %not really a method, but seemed to make the most sense near the system description.
    We propose some ideas to this end in the text we have added to the end of Section 2.1, where
    our simulations are described:
    \begin{quote}
    In consideration of our ultimate goal, which is to use high-throughput simulations to 
    facilitate our understanding of LLC membrane design for solute-specific separations, the size 
    of our system and length of the accompanying molecular simulations appears to be somewhat 
    impractical. We would like to emphasize that our large, fully atomistic models will be
    extremely valuable as a benchmark systems used to explore less expensive models. For example, we 
    could explore systems built with fewer LLC monomers by making the membrane pores shorter. We 
    could also build systems with higher concentrations of solutes in order to gather more 
    dynamical data on shorter timescales. Using what we have learned about the radial distribution
    functions of these solutes in this and our previous work\cite{}, it may be possible to 
    learn how to create initial configurations with solutes initially distributed in a way that
    is close to their equilibrium distribution, allowing solutes to thoroughly explore the 
    accessible membrane structural space more quickly and reducing the amount unequilibrated
    data that must be discarded. % could mention GCMC?
    Finally, it may be possible to speed up our simulations by 
    reducing the number of atoms using united-atom representations of the liquid crystal monomers.
    %BJC: How strong of an influence would hydrogen mass repartitioning have on hydrogen bonding?
    %, or by using hydrogen mass repartitioning to allow us to increase the MD time step.

    \end{quote}

    %r2_comment3
    \item \textit{Have the authors attempted to compare their results directly to experimental data? 
    It would be useful to clarify whether the predicted selectivities are expected to be quantitatively
    accurate or just reflect trends.}

    %BJC: This is copied straight from the reviewer response for the previous paper.
    Author reply: The reviewer makes a valid point. This work started in parallel with experimental
    work which promised solute flux and selectivities that we could compare directly to our
	simulations. However, synthesizing an aligned hexagonal phase membrane has been a practical
	challenge for our experimental collaborators and much of their focus has shifted to 
	membranes formed by liquid crystals that self-assemble into bicontinuous cubic architectures
	which are much simpler to synthesize. We have also started to shift our focus towards models 
	of the bicontinuous cubic phase, which do have much more experimental data. However, our 
	research into generating physically accurate molecular models of that phase lags our work on
	time series modeling. In future work, we will be able to apply this technique to these 
	bicontinuous systems for which we have experimental data.

    %r2_comment4    
    \item \textit{As two very minor corrections, in page 15 line 8 it should say "Method 1", and in 
    page 17 line 5 the angle should be H-D-A.}

    % BJC: reviewer is right, VMD docs are misleading: https://www.ks.uiuc.edu/Research/vmd/plugins/hbonds/
    Author reply: We thank the reviewer for pointing out our potential errors. For the hydrogen bond
    criteria we have updated the text from "D-H-A" to "H-D-A". Regarding page 15 line 8 (\textit{"Method 2:
    Since trajectories generated by Method 2..."}), changing "Method 2" to "Method 1" would actually be 
    incorrect. At the beginning of Section 2.4, we defined two techniques for generating stochastic 
    trajectories. 'Method 2' on page 15 line 8 describes the bootstrapping procedures for Method 2 of
    trajectory generation. This is a clear lack of clarity on the author's part and therefore we 
    have made an effort to avoid to change our wording to avoid confusion.

    First, we added additional clarification before describing the bootstrapping procedure (added text
    is highlighted in red):
    \begin{quote}
    Our bootstrapping procedure varied dependent on the method of trajectory generation. \textcolor{red}{
    The following procedures correspond to the methods described above:}
    \end{quote}

    We have also modified the text on page 15 line 8 from the orginal text:
    \begin{quote}
    Since trajectories generated by Method 2 are based on the clustered parameter set used to define a
    single model, we can bootstrap on trajectory ensembles of arbitrary size.
    \end{quote}
    to:
    \begin{quote}
    Since in our second approach to stochastic trajectory generation described above we use clustered 
    parameter sets to define each model, we can bootstrap on trajectory ensembles of arbitrary size.
    \end{quote}

\end{enumerate}

\bibliographystyle{ieeetr}
\bibliography{stochastic_transport}

\end{document}

% LocalWords:  Subdiffusive Solute Nanoscale Coscia leftmargin FBM vy
% LocalWords:  subdiffusion CTRW sFBM ref solutes antechamber solute
% LocalWords:  polarizable LLC intramolecular quasiharmonic BJC JCTC
% LocalWords:  tex fontsize evy Methanol's selectivities MSDDM arXiv
% LocalWords:  parametrization MSDs MSD timescales renormalizing MFPT
% LocalWords:  bicontinuous Donnan steric em dt lyotropic
% LocalWords:  subdiffusive

### 2020-08-01 Ben_Manuscripts/stochastic_transport/response_to_reviewers.tex

  %comment 5
  \item \textit{\textbf{Figure 5 page 25:} \\
		First, the symbols within the figure are very small and barely readable, and probably not
		according to authors guidelines for figures. Second, the caption, as with the other captions of
		this manuscript, contain a lot of interpretation that normally are placed in the main text. This
		might be a particular style of the authors that has its benefits, however in this specific case the
		caption fails at explaining what exactly this figure is showing. The way I interpret this figure is:
		the symbol on the y-axis marks a general parameter and the boldface symbol marks the
		parameter shown in the histogram. Am I correct? If so, I would strongly recommend modifying
		y-axis and the caption to make this clear.}

		Author reply:

		We thank the reviewer for their constructive feedback. The fontsize in the figure is indeed too small.
		We have modified the plots in the figure to have larger, more readable font. We also took this 
		opportunity to increase the font size on Figures 6--8.

		The reviewer is correct in their interpretation of the figures. For clarity, we modified the y-axes as
		well as the captions in order to further aid the reader in reading them. We also made efforts to cut
        down on the interpretation that is already presented in the main text. We made similar modifications
        to Figure 6 since it is an analogous figure. Our caption changes are presented below.

@@

        Perhaps, most importantly, Section 3.3 is primarily used to demonstrate our mathematical
        framework. Applying it to the two mode model would be trivial. We chose to use the one-mode 
        model for demonstration because it passes our qualitative and quantitative checks and is
        mathematically sound. As the reviewer points out, it is likely that our approach to 
        modeling the solute time series is not yet suitable to make quantitative predictions of 
        flux and selectivity. But our approach opens the door for applying the same analysis to 
        improved time series modeling techniques.

        Original text:
        \begin{quote}
        We do not consider the two mode AD model because it has a broken correlation structure 
        and we do not consider the MSDDM because its realizations do not display the expected 
        hopping and trapping behavior. 
        \end{quote}

        New text:
        \begin{quote}
        Although it would be trivial to test the two mode model as well, we chose not to because
        we feel the results would be misleading to the reader since the stochastic trajectories
        generated by this method lack a firm physical basis as discussed in Section 3.1.2. 
        We also do not consider the MSDDM because its realizations do not display the expected 
        hopping and trapping behavior. 
        \end{quote}

@@

	  	This may be an issue that could be overcome by developing specialized algorithms and perhaps 
	  	by using a compiled computer language like C++.

        We have modified the text to express the current limitations in a more straightforward manner:

	  	Original text:
	  	\begin{quote}
	  	The RAM requirements and performance scales greater than linearly and thus would take an 
	  	infeasible amount of memory and time to simulate transport through a pore over 100 times
        longer. 
	  	\end{quote}

	  	%MRS: scanning over this, it's probably more important to say that we probably didn't need to do it, since
                %the analytical fit was so good.
	  	Modified text:
	  	\begin{quote}
	  	At this time, it is infeasible for us to simulate transport through a pore over 100 times
	  	longer without investing significant effort into writing and optimizing new code that can
	  	handle simulation of large trajectories with correlation between all steps. 
        %BJC: added	  	
	  	However, the high quality of our fits suggests that additional effort on this front may be
	  	misplaced at this time. 
	  	\end{quote}

@@

    Author reply:

    We thank the reviewer for this suggested improvement and we have added the appropriate
    figure reference with some modifications to maintain the overall sentence flow:

    Original text:
    \begin{quote}  
    We identified three mechanisms responsible for the solute trapping behavior: 
    \end{quote}

    Modified text:
    \begin{quote}
    The complex membrane topology (see Figure~\ref{M-fig:membrane_structure}) gives rise to
    three mechanisms responsible for the solute trapping behavior: 
    \end{quote}

### 2020-08-01 Ben_Manuscripts/hdphmm/Draft.tex
Started response to reviewers for hdphmm

  We reported the mean and $1 \sigma$ confidence intervals of the MSDs based on the 
  results of 200 bootstrap trials. Our bootstrapping procedure varied dependent on the
  method of trajectory generation:
  %MRS: this is a bit confusing.  Is there an expectation these should give consistent parameters?
  %MRS: the second is boostrapping an MSD over 1000 trajectories, and the first is boostrapping an MSD over 24 trajectories.
  %MRS: these should have different amounts of noise, making them hard to compare? Is this an issue?
  %BJC: added some clarification to Method 2
  \begin{enumerate}[label={Method \theenumi :}, leftmargin=3.5\parindent]
  	\item For each bootstrap trial, we generated 24 stochastic trajectories since we
  	are constrained to sample with replacement from the 24 independent HDP-AR-HMM models.
    The result of each trial is the mean of the MSDs of the trajectories
    constituting the bootstrapped ensemble. 
    \item Since trajectories generated by Method 2 are based on the clustered parameter 
    set used to define a single model, we can bootstrap on trajectory ensembles of
    arbitrary size. For each bootstrap trial, we generated an ensemble of 1000 independent
    stochastic trajectories, calculated the MSD of each and then sampled, with replacement,
    from the ensemble. This larger ensemble allows us to achieve lower uncertainties with
    the same number of bootstrap trials as Method 1. 
  \end{enumerate}

@@

  \textit{Hydrogen bond detection}: We determined the number of hydrogen bonds 
  between each solute and the membrane as a function of time. Based on the 
  geometric criteria of Luzar and Chandler, we define a hydrogen bond to exist 
  if the distance between donor, D, and acceptor, A, atoms is less than 
  3.5\AA~and the angle formed by $D-H \cdots A$ is less than $30\degree$.~\cite{luzar_effect_1996}

>>>>

  We reported the mean and $1 \sigma$ confidence intervals of the MSDs based on the 
  results of 200 bootstrap trials. Our bootstrapping procedure varied dependent on the
  method of trajectory generation. The following procedures correspond to the methods
  described at the beginning of this section:
  \begin{enumerate}[label={Method \theenumi :}, leftmargin=3.5\parindent]
  	\item For each bootstrap trial, we generated 24 stochastic trajectories since we
  	are constrained to sample with replacement from the 24 independent HDP-AR-HMM models.
    The result of each trial is the mean of the MSDs of the trajectories
    constituting the bootstrapped ensemble.
    %r2_comment4
    \item Since in our second approach to stochastic trajectory generation described 
    above we use clustered parameter sets to define each model, we can bootstrap on 
    trajectory ensembles of arbitrary size. 
%    \item Since trajectories generated by Method 2 are based on the clustered parameter 
%    set used to define a single model, we can bootstrap on trajectory ensembles of
%    arbitrary size. 
    For each bootstrap trial, we generated an ensemble of 1000 independent
    stochastic trajectories, calculated the MSD of each and then sampled, with replacement,
    from the ensemble. This larger ensemble allows us to achieve lower uncertainties with
    the same number of bootstrap trials as Method 1. 
  \end{enumerate}

@@

  \textit{Hydrogen bond detection}: We determined the number of hydrogen bonds 
  between each solute and the membrane as a function of time. Based on the 
  geometric criteria of Luzar and Chandler, we define a hydrogen bond to exist 
  if the distance between donor, D, and acceptor, A, atoms is less than 
  3.5\AA~and the angle formed by $H-D-A$ is less than $30\degree$.~\cite{luzar_effect_1996}
